A Systematic Literature Review on Extensions to Role-Based Access Control

### 2014-02-09 paper/sections/categorization.tex
Adding note about Figure 2 and cleaning up mentions of Table 6.

We provide a definition for each observed model category based on data extracted from the primary sources and the English definitions for each noun-phrase.
Some category descriptors contain abbreviations in parenthesis that match the shortened name found within Appendix 1 \ref{tab:categorization} which presents each primary source within it's designated category.

@@

The 27 primary sources produced a set of eight hierarchical categories. 
Table \ref{tab:categorization} summarizes each primary source under their designated category and furthermore, displays the perceived hierarchy of the categories. 
Figure~\ref{fig:category_structrure} shows the hierarchy structure among categories. 
The Constraint, Organizational, Privacy, Task, and Spatial and Temporal categories can be special cases of the Context category. 
The Spatial and Temporal categories were treated as subsets of the broader category of Spatio-Temporal since this category encompasses them individually and the Spatio-Temporal category was derived from primary sources directly.

>>>>

We provide a definition for each observed model category based on data extracted from the primary sources and the English definitions for each noun-phrase.
Some category descriptors contain abbreviations in parenthesis that match the shortened name found in Table 6 (within Appendix 1) \ref{tab:categorization} which presents each primary source within it's designated category.

@@

The 27 primary sources produced a set of eight hierarchical categories. 
Table \ref{tab:categorization} summarizes each primary source under their designated category and furthermore, displays the perceived hierarchy of the categories. 
Figure~\ref{fig:category_structrure} shows the hierarchy structure among categories and the counts of primary sources for each.
For categories that have sub-categories, the totals of the category and sub-categories is provided as the second number in the figure. 
The Constraint, Organizational, Privacy, Task, and Spatial and Temporal categories can be special cases of the Context category. 
The Spatial and Temporal categories were treated as subsets of the broader category of Spatio-Temporal since this category encompasses them individually and the Spatio-Temporal category was derived from primary sources directly.
